---
title: "Data Exploration Assignment Due - 4th week of October"
author: "Shreya and Francis"
date: "October 14, 2017"
output: html_document
---

## Action Needed by Francis (opened by Shreya)
@Franics - Please review updated versions in the Deliver.Rmd 

Also, one thing to may be consider in there is to check that we change before the particular date when this gre score system was used, irrespective of the system, we need to consider that well. - Thoughts on this Francis?

Could you please update when you have the regression thing you are working on and the data exploration part as well!

Following code is for your reference Francis - Since you showed interest in merging data. 
```{r}
library(dplyr)
library(tidyr)
login$count <- 1
login2 <- login %>% group_by(identity) %>% summarize(sum(count))
```
```{r}
library(corrplot)
COR <- cor(gre) 
corrplot(COR, order="AOE", method="circle", tl.pos="lt", type="upper", tl.col="black", tl.cex=0.6, tl.srt=45, addCoef.col="black", addCoefasPercent = TRUE, sig.level=0.50, insig = "blank")
```


## Action Needed by Shreya (Please add any concerns or questions for Shreya here)









## Read_Files
Please review updated versions in the Deliver.Rmd

## Gre
Remove Student with identity code "90584", Reason: 0 GRE score information on quantitative aptitude
Please review updated versions in the Deliver.Rmd

## Event_Attendance
Please review updated versions in the Deliver.Rmd

## Application_Decision
Please review updated versions in the Deliver.Rmd

## Application Base
Please review updated versions in the Deliver.Rmd

## Login Data
Please review updated versions in the Deliver.Rmd

## Message Data
Please review updated versions in the Deliver.Rmd

## Starting with Merging data
Please review updated version in the Deliver.Rmd

## Phase I - Barplots and Histograms
Please review updated version in the Deliver.Rmd
